My graduate work would not have been possible without the help and support of many people. First and foremost I want to acknowledge my advisor, Arjun Yodh. I have learned a lot from Arjun over the years and I still strive to emulate his ability to think outside the box when problem solving. His deep knowledge of not just the biomedical optics field but nonlinear optics and soft condense matter physics is very apparent when discussing how to approach various problems. Arjun has always been generous with his time and advice and I will always be thankful for that.

I want to thank my collaborators as well. I've had the honor of being able to work with world class researchers like John Schotland, Manabu Machida, and Vadim Markel. Vadim was always patient in teach me about image reconstructions and it has been a pleasure to work closely with him. I also want to thank Simon Arridge and Martin Schweiger for their work on the Gen3 imager project. I am especially thankful to Martin for enduring hot summers in Philadelphia to work to produce our images and for spending time teaching me about nonlinear reconstruction methods. I also want to thank Mitchell Schnall, Brian Czerniecki, and Emily Conant without whom our clinical work would not be possible.

When I first joined Arjun's lab I worked with Kijoon Lee. Kijoon got me started at the lab and really went out of his way to help me learn about diffuse optics and instrumentation. I could tell that he really loved to teach. Kijoon soon left for Singapore and I was certainly poorer for not being able to learn more from him before he left. It was only a few months but I also got to meet with Alper Corlu, Chao Zhou, Jonathan Fisher, and Guoqiang Yu all who warmly welcomed me into the lab.
    
In my earlier years Dr. Regine Choe and Turgut Durduran were truly Arjun's lieutenants and advised all of the graduate students. They really shaped my early graduate experience and I learned a great deal from them. In particular Regine really got me started in learning about breast imaging.
    
There were many people who worked with me on breast imaging over the years and helped me get over a lot of hurdles. I want to thank the numerous clinical coordinators like Maddie Winters, Sarah Grundy, and Alex Vandergrift who recruited patients and made sure they were comfortable. I want to thank Darren for his enthusiasm, relentless energy, and drive. I also remember interesting nights at Perelman with Bryan Chong and sharing stories in the dark while taking data. Jeff is also one of my peers who I've felt a kinship in instrumentation work. My only regret is that I did not work with him more over the years. Dr. Frank Moscatelli was one of the few people who called things as it is and I have him to thank for teaching me people skills. I cannot forget Jaka who was here for a short time but became one of my closest friends. I also want to thank Sophie Chung, Sarauv Pathak and Soren Konecky as well.

Then there are those who I consider good friends who made coming into the lab a lot of fun. Meeri Kim is (probably) up there in best friends of all time. Erin Buckley and I (along with Meeri) have shared a few pet rodents together and that is a strong bond that cannot be broken (R.I.P. hamster JD). Wes Baker has always been a good friend who always made me laugh every time he joked around and who always made it more fun to hang out if he was around. Jennifer Lynch was always a comrade in arms and the best fashion advisor and life cheerleader anyone could ask for. Steve (or Sam) Schenkel for the workout sessions and just being a great guy to hang out with. Tiffany Ko for living life in a way that I envied. I want to thank Ken Abrahmson as well for great conversation and being our lab's Q.

I want to acknowledge David Busch who gave countless (often unsolicited) advice that was incredibly helpful academically and personally. I owe him more than I'd like to admit and I really cherish his friendship. Ashwin Parthasarathy has been a friend from day one. I have him to thank for many great conversations, ideas, and really fun moments in the office. I want to also thank Venki Kauri because he saved my life. I've known him less than a year but Venki really brought a great surge of curiosity and love of diffuse optics that one can only describe as contagious. I want to thank other people who have really shaped my time here in the lab like Rickson Mesquita, ShihYu Tzeng, Zhe Li, Detian Wang, Alex Zhang, Julien Menko, and Leonid Zubkov.

Finally I want to thank my family for their support throughout these years. They've always encouraged me from when I tried to be a cellist to when I decided to become a physicist. Thank you mom and dad for your constant love and encouragement. Thank you all for making this work possible.